Large scale risks from pesticides in small streams

### 2016-11-13 article.tex
revised comparison with stehle & Schulz

%%%! den absatz hier nochmal überarbeiten
Compared to \citet{stehle_pesticide_2015} we found lower rates of RAC exceedances (5\% (n = 39,609) vs 37.1\% (n = 1,352) of measurements above LOQ). 
This may be attributed to several differences: i) Different compound spectra. \citet{stehle_pesticide_2015} analysed 23 insectices, we 107 pesticides of different groups. ii) Different objectives of governmental monitoring and scientific studies. Scientific studies may be slightly biased towards streams with high pollution to detect effects, whereas monitoring aims mainly at spatially representative surveillance of water quality, also during periods of lower pesticide usage and at natural sites. iii) Different sampling strategies. The dataset compiled here comprised only samples from grab sampling, which may considerably underestimate pesticide exposure \citep{stehle_probabilistic_2013}. 
%%%! den absatz hier nochmal überarbeiten

>>>>

Compared to \citet{stehle_pesticide_2015} we found higher rates of RAC exceedances for insecticides.
They found exceedances in 37.1\% of measurements \textgreater LOQ (n = 1352, 23 insecticides), whereas, we found exceedances in 67\% of measurements \textgreater LOQ (n = 1855, 22 insecticides).
This could be attributed to different insecticides considered and different underlying RACs.
Our study has only 7 insecticides with RACs in common with the insecticides investigated by \citet{stehle_pesticide_2015}.
Moreover, all RACs were lower in our study (mean = -0.71 $\mu g/L$, range = [-2.7570; -0.0045]). 
Nevertheless, it must be noted that the dataset compiled here comprised only samples from grab sampling, which may considerably underestimate pesticide exposure \citep{stehle_probabilistic_2013, Xing_Chow_Rees_Meng_Li_Ernst_Benoy_Zha_Hewitt_2013}.
